\section{Introduction}
\label{sec:introduction}

\subsection{Context and Problem Statement}

Sleep disorders and poor sleep quality represent a growing concern in clinical environments,
particularly for patients undergoing long-term care. Traditional monitoring methods often
require intrusive equipment or fail to provide real-time, actionable data to healthcare
providers. Furthermore, existing therapeutic interventions are rarely personalized or adjustable, limiting the ability of medical staff to respond to a
patient's evolving needs. This project addresses these gaps by developing an integrated
IoT system that combines passive sleep monitoring with active, non-invasive sound-based
therapy, all managed through a connected digital platform.

\subsection{Geographic Scale and Users}

The system is designed for deployment within medical facilities, such as hospitals or
sleep clinics, where patients are under the supervision of healthcare professionals.
At the local level, each patient interacts with two hardware devices: a wearable headband
worn during sleep and a bedside gateway unit. At the institutional level, doctors and
nurses access a centralized web application to monitor all patients under their care and
issue adjustments remotely. The infrastructure is cloud-hosted, allowing it
to scale across multiple wards or facilities and to support concurrent access by numerous
medical staff members from any location with internet connectivity.

\subsection{Relevance and Real-World Applications}

Bone conduction technology offers a non-invasive means of delivering therapeutic audio
stimulus without disturbing a patient's sleep environment. Combined with
heart rate and blood oxygen saturation (SpO2), the system
enables an efficient approach to sleep therapy: data is collected, transmitted to the
cloud in real time, and visualized by clinicians who can then fine-tune treatment
parameters remotely. This approach reduces the need for physical intervention during
nighttime hours, improves the responsiveness of care, and generates longitudinal data
that can inform future treatment decisions. The system is equally applicable to home-care
scenarios, where the gateway's Bluethooth configuration via smartphone lowers the barrier to
autonomous setup by patients.

\subsection{Main Objectives}

The main objectives of this system are as follows:
\begin{itemize}
    \item Monitor patient sleep quality in real time through movement, heart rate, and SpO2
          measurements collected by a wearable ESP32-based headband.
    \item Deliver personalized, non-invasive sleep therapy via bone conduction sound waves,
          with frequencies adjustable remotely by a supervising physician.
    \item Transmit physiological data reliably from the wearable device to the cloud using
          ESP Now to a local gateway and the MQTT protocol for server communications.
    \item Provide clinicians with a real-time web dashboard to monitor all patients, review
          historical trends stored in a time-series database, and issue soundwave adjustments.
    \item Enable straightforward deployment and configuration through a smartphone-assisted
          Bluetooth setup of the gateway device.
\end{itemize}